---
title: "Test with Poloniex API"
output: html_notebook
---

## Test with poloniex API

## List of currency pairs:

US Dollars - Cryptocurrencies Markets:

# BITCOIN CASH
usdt_bch
# BITCOIN
usdt_btc
# ETHEREUM
usdt_eth
# ETHEREUM CLASSIC
usdt_etc
# LITECOIN
usdt_ltc
# ZCASH
usdt_zec
# RIPPLE
usdt_xrp
# MONERO
usdt_xmr
# STELLAR
usdt_str
# DASH
usdt_dash
# NXT
usdt_nxt
# AUGUR
usdt_rep


##Up-to-date code (for final version)

```{r}
library(jsonlite)
library(glue)
library(httr)

library(lubridate)
library(xts)

library(dplyr)
library(tidyr)
library(dygraphs)
library(stringr)
```



```{r}
market <- function(currencyPair) {

  url <- glue("https://poloniex.com/public?command=returnChartData&currencyPair={currencyPair}&start=1435699200&end=9999999999&period=14400")
  
  #res <- GET(url)
  
  dataset <- fromJSON(url)
  
  dataset$date <- as_datetime(dataset$date)
  
  prices <- xts(dataset$open,dataset$date)
  
  #volumes <- xts(dataset$volume,dataset$date)
  
  prices %>% dygraph()
  
}

```

```{r}
market(currencyPair = "USDT_ETH")
```


## Previous code working:

```{r}
currencyPair = "USDT_BTC"

url <- glue("https://poloniex.com/public?command=returnChartData&currencyPair={currencyPair}&start=1435699200&end=9999999999&period=14400")
  
res <- GET(url)
```


```{r}
fromJSON(url)
```

Here we see that the date is in a UTC seconds format.
We need a library to convert it in normal dates. The library "lubridate" can help us.

```{r}
dataset <- fromJSON(url)
```

Converting into datetime:

```{r}
dataset$date <- as_datetime(dataset$date)
```

And then creating a time-series:

```{r}
open_price <- xts(dataset$open,dataset$date)

open_price %>% dygraph()

```



## Quick test on webscraping


```{r}
library(rvest)
```

```{r}
Description_function <- function(CryptoName) {

  url <- glue("https://coinpedia.org/currency/{CryptoName}") %>%
    read_html()

  text <- html_nodes(url,'.elementor-text-editor p') %>% html_text()
  
}
```

```{r}
description <- Description_function("litecoin")
```

```{r}
description
```
