---
title: "Test with Poloniex API"
output: html_notebook
---

## Test with poloniex API

## List of currency pairs:

US Dollars - Cryptocurrencies Markets:

## BITCOIN CASH
usdt_bch
## BITCOIN
usdt_btc
## ETHEREUM
usdt_eth
## ETHEREUM CLASSIC
usdt_etc
## LITECOIN
usdt_ltc
## ZCASH
usdt_zec
## RIPPLE
usdt_xrp
## MONERO
usdt_xmr
## STELLAR
usdt_str
## DASH
usdt_dash
## NXT
usdt_nxt
## AUGUR
usdt_rep


```{r}
library(jsonlite)
library(glue)
library(httr)

library(lubridate)
library(xts)

library(dplyr)
library(tidyr)
library(dygraphs)
library(stringr)
```



```{r}
market <- function(currencyPair) {

  url <- glue("https://poloniex.com/public?command=returnChartData&currencyPair={currencyPair}&start=1435699200&end=9999999999&period=14400")
  
  res <- GET(url)
  
  dataset <- fromJSON(url)
  
  dataset$date <- as_datetime(dataset$date)
  
  prices <- xts(dataset$open,dataset$date)
  
  #volumes <- xts(dataset$volume,dataset$date)
  
  prices %>% dygraph()
  
}

```

```{r}
market(currencyPair = "USDT_BCH")
```

```{r}
currencyPair = "usdt_btc"

url <- glue("https://poloniex.com/public?command=returnChartData&currencyPair={currencyPair}&start=1435699200&end=9999999999&period=14400")
  
res <- GET(url)
```


```{r}
fromJSON(url)
```

Here we see that the date is in a UTC seconds format.
We need a library to convert it in normal dates. The library "anytime" can help us.

```{r}
dataset <- fromJSON(url)
```

```{r}

```

```{r}
dataset$date <- as_datetime(dataset$date)
```

```{r}
open_price <- xts(dataset$open,dataset$date)

open_price %>% dygraph()

```



## The function "anytime" converts properly the UTC seconds time into a UTC time.

```{r}

```


```{r}
prices <- dataset %>%
  select(date,open,close)

#View(open_price)

#class(open_price)

prices %>% 
  #group_by(date,open) %>%
  dygraph()

#  dygraph(xlab = date, ylab = open)
```


```{r}
?data.frame
```

```{r}

```

